PLAE web app enables powerful searching and multiple visualizations across one million unified single-cell ocular transcriptomes

### 2022-09-09 manuscript_00.Rmd
latest version

```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
#knitr::opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
knitr::opts_chunk$set(out.width = '100%', dpi=300)
library(tidyverse)
library(citr)
library(cowplot)
library(ggrepel)
library(colorspace)
library(flextable)
library(captioner)
library(glue)
library(tictoc)
#tic()()
#data_dir_vGiga <- '/Volumes/McGaughey_S/data/scEiaD/'
#data_dir_vPLAE <- '/Volumes/McGaughey_S/data/scEiaD_2022_02/'
#data_dir_vGiga <- '~/data/scEiaD_gigascience/'
#data_dir_vPLAE <- '~/data/scEiaD_2022_02/'
data_dir_vGiga <- '/Volumes/Thunder/data/scEiaD/'
data_dir_vPLAE <- '/Volumes/Thunder/data/scEiaD_2022_02/'
# setup caption-ing
fig_cap <- captioner("Figure")
supFig_cap <- captioner("Supplemental Figure")
tab_cap <- captioner("Table")
supTab_cap <- captioner("Supplemental Table")

@@

#data_dir_vGiga <- '/Volumes/McGaughey_S/data/scEiaD/'
#data_dir_vPLAE <- '/Volumes/McGaughey_S/data/scEiaD_2022_02/'
#data_dir_vGiga <- '~/data/scEiaD_gigascience/'
#data_dir_vPLAE <- '~/data/scEiaD_2022_02/'
data_dir_vGiga <- '/Volumes/Thunder/data/scEiaD/'
data_dir_vPLAE <- '/Volumes/Thunder/data/scEiaD_2022_02/'

>>>>

```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
#knitr::opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
knitr::opts_chunk$set(out.width = '100%', dpi=300)
library(tidyverse)
library(citr)
library(cowplot)
library(ggrepel)
library(colorspace)
library(flextable)
library(captioner)
library(glue)
library(tictoc)
#tic()()
#data_dir_vGiga <- '/Volumes/McGaughey_S/data/scEiaD/'
#data_dir_vPLAE <- '/Volumes/McGaughey_S/data/scEiaD_2022_02/'
data_dir_vGiga <- '~/data/scEiaD_gigascience/'
data_dir_vPLAE <- '~/data/scEiaD_2022_02/'
#data_dir_vGiga <- '/Volumes/Thunder/data/scEiaD/'
#data_dir_vPLAE <- '/Volumes/Thunder/data/scEiaD_2022_02/'
# setup caption-ing
fig_cap <- captioner("Figure")
supFig_cap <- captioner("Supplemental Figure")
tab_cap <- captioner("Table")
supTab_cap <- captioner("Supplemental Table")

@@

#data_dir_vGiga <- '/Volumes/McGaughey_S/data/scEiaD/'
#data_dir_vPLAE <- '/Volumes/McGaughey_S/data/scEiaD_2022_02/'
data_dir_vGiga <- '~/data/scEiaD_gigascience/'
data_dir_vPLAE <- '~/data/scEiaD_2022_02/'
#data_dir_vGiga <- '/Volumes/Thunder/data/scEiaD/'
#data_dir_vPLAE <- '/Volumes/Thunder/data/scEiaD_2022_02/'
